An ethnographic study of an empirical software engineering lab

### 2023-10-02 Article.tex
Last requirements
Some changes motivated by the Editor Chief's comments.
Tittle change
Last changes of the title

\title{How does an Experimental Software Engineering Lab Work? An Ethnographic Study}

@@

\section*{Acknowledgment}
This work was supported by the project PGC2018-097265-B-I00 funded by the Spanish Ministry of Science and Innovation and co-financed by FEDER, and the Universidad de las Fuerzas Armadas  - ESPE's Grupo de Investigación en Modelos de Producción de Software e Industria Inteligente (GrIMPSoftII).

>>>>

\title{An ethnographic study of an empirical software engineering lab}

@@

\section*{Acknowledgment}
This work was supported by the project PGC2018-097265-B-I00 funded by the Spanish Ministry of Science and Innovation and co-financed by FEDER and the Universidad de las Fuerzas Armadas  - ESPE's Grupo de Investigación en Modelos de Producción de Software e Industria Inteligente (GrIMPSoftII). This work's preprint has been published \cite{Fonseca-2023-experimentation-proccess-SE-unpublished}.
